### 2021-09-02 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
BL comments

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. High efficiencies, in some simple recompression cycles reaching 50\% efficiency, allow for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.  Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.

A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day. Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2012, turchi_2013, ho_2015, wang_2018}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch. A LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 595 $^{\circ}$C. LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} . In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.

Various studies on complimentary solar-nuclear systems have been accomplished with several presented as follows. Monnerie et al. (2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.  Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}. Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper. Implementation of a combined solar and nuclear plant, modeled in the Wang et al. (2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.  This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative. Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a suplementary CSP TES charging technique.

@@

\subsection{Cycle Component Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques and are discussed in more detail below. Turbines and compressors are analyzed using isentropic efficiencies. Counter-flow heat exchangers use the effectiveness-NTU method while simplified ``black box'' heat exchangers use a simple energy balance for state point calculations. The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.

@@

\subsubsection{Lead-Cooled Fast Reactor}
%--------------------------------------------------------------------------------------
Lead-cooled fast reactors use energy from a controlled nuclear reaction to heat molten lead. This lead is used to both cool the core as well as transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}. The lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX. The inlet, outlet and heat transfer rates are defined by our industry partner, Westinghouse Electric Company making the black box simplification viable. The energy balance for the black box assumption can be seen in Equation \ref{eq-lfr-black-box}.

@@

Where the left hand side, $\dot{m}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C. 
%\mw{Make sure numbers are in math mode -BW}
The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side. Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by our industry partner.
%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.

@@

\hl{The C2S heat exchanger is active in the 'charging' cycle configurations, when the focus is on heat storage for later use. Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle. Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver then being stored in the hot TES.}
%\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }

'Non-charging' cycle configurations are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity. When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.

@@

Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The constrained study is calculated by setting the LFR inlet temperature to the design value of $400^{\circ}$C, which is a requirement of the LFR primary circuit to maximize power output within material limits. In addition to the constrained studies, unconstrained studies are required to test the penalties that LFR inlet temperature has on efficiency. The unconstrained study is performed by gradually increasing the mass flow to the main compressor through a parametric study while maximizing cycle efficiency. In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post. 
%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}

@@

%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

In the third case the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to $380^{\circ}$C. The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX increasing dispatchability.
%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability -BW}

@@

Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency \mw{compared to...?}. To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired. This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines. The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR1. 
%\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
The cycle with heat addition from the CSP also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2. 
\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.} 
After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
\bl{this is more about having a compromise option of intermediate complexity and efficiency}

@@

The C2S heat exchanger is located around the turbine and LFR at 7A to 8A depending on the charging configuration: pre, post, parallel or circulator. Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint. The two constrained studies have varied cold CSP TES temperature with the lowest temperature of $390^{\circ}$C and highest temperature of $440^{\circ}$C. The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.  
\bl{this is clearer than the previous one but bullets could still be useful}

@@

Charging cycle configurations accommodate energy storage modes of operation. These configurations examine the location of LFR heat extraction via the SALT HX. To maximize the available heat for extraction, alternator net power is set to zero, therefore requiring that the turbine power is equal to the compressors' demand. Despite the components being non-ideal and consuming power, the recompression cycle continues to operate, ensuring that there is mass flow to transfer heat from the Brayton cycle to C2S. The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases. The location of heat extraction in the cycle is compared within the C-LFR-ON Brayton cycle by placing the salt heat exchanger in different locations around the turbine. To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.  
%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}

@@

%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}

>>>>

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allowing them to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument}
Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.  Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.

\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton? In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common}
A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day. Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2012, turchi_2013, ho_2015, wang_2018}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch. An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C. LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} \bl{If you are reading this reference https://www.osti.gov/servlets/purl/1108068 I think the loop is in Sandia National Lab and the conference where the paper was published was in Boulder}. In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.

\bl{I would bullet out the next three citations}
Various studies on complimentary solar-nuclear systems have been accomplished with several presented as follows. Monnerie et al. (2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.  Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}. Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper. Implementation of a combined solar and nuclear plant, modeled in the Wang et al. (2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.  This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative. Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a suplementary CSP TES charging technique. 
\bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences). You could start by saying that it is prior work on the LFR-CSP-sCO2 concept. Then describe its cycle configuration with the high temperature salt. Then in the following sentence (the stuff you currnetly have highlighted) you can say that your work is investigating higher lead temperatures than Wang (because of Westinghouse LFR) and lower temperature salt (technology readiness) and this leads to very different cycle configurations and options than Wang, as will be discussed. The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang}

@@

\subsection{Cycle Component Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques and are discussed in more detail below. Turbines and compressors are analyzed using isentropic efficiencies. Counter-flow heat exchangers are modelled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data is available. The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.
\bl{does above make this clearer?}

@@

\subsubsection{Lead-Cooled Fast Reactor}
%--------------------------------------------------------------------------------------
Lead-cooled fast reactors use energy from a controlled nuclear reaction to heat molten lead. This lead is used to cool the core and transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}. The lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX. The inlet, outlet and heat transfer rates were provided by Westinghouse, making the black box simplification viable. The energy balance for the black box assumption can be seen in Equation \ref{eq-lfr-black-box}.

@@

Where the left hand side, $\dot{m}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C. 
%\mw{Make sure numbers are in math mode -BW}
The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side. Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by Westinghouse.
%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.

@@

\hl{The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use. Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle. Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver then being stored in the hot TES.}
%\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }

'Non-charging' cycle operating modes are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity. When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.

\bl{I don think the above covers the case where the salt discharges. It might be worth eliciting how the operating modes change as power demand increases. From highest to lowest demand. In all modes CSP will charge the salt is sun is available: (1) LFR and S2C both dispatch, maximum power (2) As power demand decreases, S2C ramps down until no power dispatched through salt (i.e. salt is charged) (3) LFR dispatches, no dispatch from S2C (4) LFR ramps down and gradually transfers greater and greater fraction of power to salt using C2S. (5) No electricity dispatched, all LFR heat passes through C2S
}

@@

Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The constrained study is calculated by setting the LFR inlet temperature to the design value of $400^{\circ}$C, which is a requirement of the LFR primary circuit to maximize power output within material limits. In addition to the constrained studies, unconstrained studies are required to test the penalties that LFR inlet temperature has on efficiency. The unconstrained study is performed by gradually increasing the mass flow to the main compressor through a parametric study while maximizing cycle efficiency. In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post. 
%%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}

@@

%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

In the third case the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to $380^{\circ}$C. The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX increasing dispatchability.
%%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability -BW}

@@

Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency \mw{compared to...?}. To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired. This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines. The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR1. 
%\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
The cycle with heat addition from the CSP also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2. 
\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.} 
After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
%\bl{this is more about having a compromise option of intermediate complexity and efficiency}

@@

The C2S heat exchanger is located around the turbine and LFR at 7A to 8A depending on the charging configuration: pre, post, parallel or circulator. Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint. The two constrained studies have varied cold CSP TES temperature with the lowest temperature of $390^{\circ}$C and highest temperature of $440^{\circ}$C. The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.  
%\bl{this is clearer than the previous one but bullets could still be useful}

@@

Charging cycle configurations accommodate energy storage modes of operation. These configurations examine the location of LFR heat extraction via the SALT HX. To maximize the available heat for extraction, alternator net power is set to zero, therefore requiring that the turbine power is equal to the compressors' demand. Despite the components being non-ideal and consuming power, the recompression cycle continues to operate, ensuring that there is mass flow to transfer heat from the Brayton cycle to C2S. The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases. The location of heat extraction in the cycle is compared within the C-LFR-ON Brayton cycle by placing the salt heat exchanger in different locations around the turbine. To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.  
%%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}

@@

%%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
